Estimating duration in the presence of misclassification

### 2024-01-04 cis-imperfect-testing.tex
Figure with ntot posterior sensitivity

The assumption that the estimates are most sensitive to is the strength of the prior on $\ntot$.
A very weak, almost uninformative, prior on this quantity causes the posterior estimate to be much higher than the estimate from \textcite{birrellRTM2}.
When increasing the prior's strength, the posterior estimate moves towards the prior smoothly, as expected (see\todo{figure showing $r$ vs $\ntot$}).
Taking a prior from \textcite{birrellRTM2} means that the posterior survival is close to the \cref{E-ATACCC} estimate in the region where that estimate is reliable.
This justifies the use of this prior.

>>>>

The assumption that the estimates are most sensitive to is the strength of the prior on $\ntot$.
A very weak, almost uninformative, prior on this quantity causes the posterior estimate to be much higher than the estimate from \textcite{birrellRTM2}.
When increasing the prior's strength, the posterior estimate moves towards the prior smoothly, as expected (see \cref{imperf-test:fig:ntot}).
Taking a prior from \textcite{birrellRTM2} means that the posterior survival is close to the \cref{E-ATACCC} estimate in the region where that estimate is reliable.
This justifies the use of this prior.
\begin{figure}
  \centering \includegraphics{cis-imperfect-testing/CIS_ntot}
  \caption{How the posterior estimate of $\ntot$ changes with the value of $r$ in the prior on $\ntot$.}
  \label{imperf-test:fig:ntot}
\end{figure}
